Bayesian multi-proxy reconstruction of early Eocene latitudinal temperature gradients

### 2023-08-10 manuscript/main.qmd
more SM, reviewer replies

Geochemical climate proxy data were extracted from a latest Paleocene and early Eocene compilation [@Hollis2019]. This compilation provides data on four different geochemical proxies for reconstructing seawater temperature: &delta;^18^O, &Delta;~47~, Mg/Ca and TEX~86~. For our analyses, this dataset was restricted to the EECO (defined as 53.8 -- 49.1 Ma) and samples from the continental shelf. Recrystallised &delta;^18^O samples were also excluded as secondary diagenetic calcite precipitated after deposition can bias isotope measurements and offset temperature values [@Schrag1999]. This filtering resulted in most &delta;^18^O samples being excluded from the dataset (retaining 8 out of 152). After data filtering, `r n_geochem` geochemical proxy samples from `r n_geochem_location` locations remained. For a detailed description of each proxy see @Hollis2019.

>>>>

Geochemical climate proxy data were extracted from a latest Paleocene and early Eocene compilation [@Hollis2019]. This compilation provides sea surface temperature data on four different geochemical proxies for reconstructing seawater temperature: &delta;^18^O, &Delta;~47~, Mg/Ca and TEX~86~. For our analyses, this dataset was restricted to the EECO (defined as 53.8 -- 49.1 Ma) and samples originating from near the ocean surface or mixed layer. Samples labelled as "thermocline" or "sub-thermocline" were excluded. Recrystallised &delta;^18^O samples were also excluded as secondary diagenetic calcite precipitated after deposition can bias isotope measurements and offset temperature values [@Schrag1999]. This filtering resulted in most &delta;^18^O samples being excluded from the dataset (retaining 8 out of 152). After data filtering, `r n_geochem` geochemical proxy samples from `r n_geochem_location` locations remained. For a detailed description of each proxy see @Hollis2019.
